From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-05-10 paper.tex
Brayns

@@

The rendering applications form the backbone of our ecosystem.

\subsection{Interactive Raytracing}

\subsection{OpenGL Parallel Rendering}

\subsection{Out-of-Core Volume Rendering}

>>>>

\FIXME{teaser gallery}

@@

The rendering applications form the backbone of our ecosystem. They cover a
wide range of established rendering algorithms to serve a broad set of use
cases for visual debugging, scientific illustrations and outreach.

\subsection{Brayns: Interactive Raytracing}

Advances in computer hardware and software have brought raytracing to the point
where it replaces classical rasterization for virtually all use cases in
scientific visualization. On one hand, local illumination for typical OpenGL
data sets (up to hundred million triangles) can be done at similar framerates
to OpenGL~\cite{ospray}. For small datasets, OpenGL performs better, but for
larger data sets raytracing outperforms OpenGL. This is due to a better
scalability with respect to the data set size ($O(\log{N})$ vs $O(n)$).
Furthermore, CPU-based raytracing allows the rendering of larger data sets
without any level-of-detail algorithms due to the larger memory size. Last, but
not least, advanced rendering algorithms such as shadowing, reflections and
global illuminations are significantly easier to implement in a raytracer.

It is for these reasons that interactive raytracing is the future technology for
interactive and offline rendering at Blue Brain. We have developed a first open
source implementation of a visualization engine with different backends:
OSPRay~\cite{ospray} for CPU-based raytracing and OptiX~\cite{optix} for
GPU-based raytracing. These application called Brayns can load and visualize
our data sets in a variety of modes and integrates with our messaging solution
to be accessible from Python.

\FIXME{teaser gallery}

\subsection{RTNeuron: OpenGL Parallel Rendering}

\subsection{Livre: Out-of-Core Volume Rendering}
